\begin{abstract}
The rapid digitization of business processes has created an urgent need for secure mechanisms to authenticate and verify digital documents. Traditional paper-based document signing is inherently inefficient, time-consuming, and incompatible with modern digital workflows. Furthermore, digital documents transmitted over networks are vulnerable to forgery, tampering, and unauthorized modifications, raising significant legal and security concerns regarding document authenticity.

This project presents the design and implementation of a Document Signer System, an enterprise-grade secure digital signature solution built as a full-stack web application. The system employs RSA-2048 cryptographic algorithms with SHA-256 hashing to generate mathematically verifiable digital signatures that guarantee document authenticity, integrity, and non-repudiation. The application follows a layered Model-View-Controller architecture using Python and the Django web framework for the backend, SQLite for secure data persistence, and a modern dark-themed web interface for user interaction.

The system provides comprehensive functionality including user registration with automatic cryptographic key pair generation, secure document upload and storage, digital signature creation using the signer's private key, and real-time signature verification with tamper detection capabilities. Experimental results demonstrate that the system successfully detects unauthorized document modifications and validates authentic signatures with complete accuracy. This project establishes a practical foundation for secure digital document processing and contributes to addressing real-world challenges of document forgery in digital environments.

\vspace{0.5cm}
\noindent\textbf{Keywords:} Digital Signature, RSA Cryptography, Document Authentication, Tamper Detection, Django, SHA-256, Data Integrity
\end{abstract}

\clearpage
