\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{References}

\bibitem{rivest1978}
R.~L. Rivest, A.~Shamir, and L.~Adleman, ``A Method for Obtaining Digital Signatures and Public-Key Cryptosystems,'' \textit{Communications of the ACM}, vol.~21, no.~2, pp.~120--126, 1978.

\bibitem{diffie1976}
W.~Diffie and M.~Hellman, ``New Directions in Cryptography,'' \textit{IEEE Transactions on Information Theory}, vol.~22, no.~6, pp.~644--654, 1976.

\bibitem{stallings2017}
W.~Stallings, \textit{Cryptography and Network Security: Principles and Practice}, 7th~ed. Pearson Education, 2017.

\bibitem{nist2020dss}
National Institute of Standards and Technology, ``Digital Signature Standard (DSS),'' FIPS PUB 186-4, U.S. Department of Commerce, 2020.

\bibitem{nist2020shs}
National Institute of Standards and Technology, ``Secure Hash Standard (SHS),'' FIPS PUB 180-4, U.S. Department of Commerce, 2020.

\bibitem{django2024}
Django Software Foundation, ``Django Documentation,'' Version 4.2, 2024. [Online]. Available: \url{https://docs.djangoproject.com/}

\bibitem{cryptography2024}
Python Cryptographic Authority, ``Cryptography Library Documentation,'' 2024. [Online]. Available: \url{https://cryptography.io/}

\bibitem{pkcs1}
RSA Laboratories, ``PKCS \#1 v2.2: RSA Cryptography Specifications,'' RSA Security Inc., 2012.

\bibitem{menezes2018}
A.~J. Menezes, P.~C. van Oorschot, and S.~A. Vanstone, \textit{Handbook of Applied Cryptography}. CRC Press, 2018.

\bibitem{itact2000}
Ministry of Electronics and Information Technology, Government of India, ``Information Technology Act, 2000,'' New Delhi, India, 2000.

\end{thebibliography}
